Supplement to Explore the factors that may be associated with obesity

### 2024-05-04 Rcode/mlmodel-code/ml-model-v1.qmd
some minor errors

@@

+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Model                             | Predictor                                                     | Metric Value  | Metric Value on testing data |
+===================================+===============================================================+===============+==============================+
| Linear null                       | \-                                                            | RMSE=8.01     | RMSE=7.99                    |
+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Linear regression 1               | Age, History, Alcohol, MTRANS                                 | RMSE=0.62     | RMSE=6.54                    |
+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Linear regression 2               | All                                                           | RMSE=6.29     | RMSE=3.81                    |
+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Linear regression 2 + LASSO model | All                                                           | RMSE=6.34     | RMSE=6.47                    |
|                                   |                                                               |               |                              |
|                                   |                                                               | l=0.023       |                              |
+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Random forest                     | All                                                           | RMSE=3.35     | RMSE=3.97                    |
+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Logistic null                     | \-                                                            | Accuracy=0.17 | Accuracy=0.15                |
+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Discriminant analysis             | Gender, Age, History, Water, Alcohol, FAF, MTRANS, Gender_Age | Accuracy=0.50 | Accuracy=0.50                |
+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Multinominal logistic regression  | All                                                           | Accuracy=0.55 | Accuracy=0.50                |
+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+

@@

# Update the formula to include Age, History, Alcohol, and MTRANS as predictors
formula_lm1_test <- paste("BMI ~ Age + History + Alcohol + MTRANS")

@@

# Print the accuracy
print(paste("Accuracy of the DA model on test data:", accuracy_DA_test))
```
I will explore more information for LASSO model.
```{r}
# Extract coefficients from the fitted LASSO model
lasso_coefficients <- coef(lasso_model_optimal)

>>>>

# Initialize variables to store results
minRMSE1 <- Inf
bestSubset1 <- NULL

@@

+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Model                             | Predictor                                                     | Metric Value  | Metric Value on testing data |
+===================================+===============================================================+===============+==============================+
| Linear null                       | \-                                                            | RMSE=8.01     | RMSE=7.99                    |
+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Linear regression 1               | Gender, Age, History, Water, Alcohol, FAF, MTRANS             | RMSE=6.42     | RMSE=6.54                    |
+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Linear regression 2               | All                                                           | RMSE=6.29     | RMSE=3.81                    |
+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Linear regression 2 + LASSO model | All                                                           | RMSE=6.34     | RMSE=6.47                    |
|                                   |                                                               |               |                              |
|                                   |                                                               | l=0.023       |                              |
+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Random forest                     | All                                                           | RMSE=3.35     | RMSE=3.97                    |
+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Logistic null                     | \-                                                            | Accuracy=0.17 | Accuracy=0.15                |
+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Discriminant analysis             | Gender, Age, History, Water, Alcohol, FAF, MTRANS, Gender_Age | Accuracy=0.50 | Accuracy=0.50                |
+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Multinominal logistic regression  | All                                                           | Accuracy=0.55 | Accuracy=0.50                |
+-----------------------------------+---------------------------------------------------------------+---------------+------------------------------+

@@

# Update the formula
formula_lm1_test <- paste("BMI ~ Gender + Age + History + Water + Alcohol + FAF + MTRANS")

@@

# Print the accuracy
print(paste("Accuracy of the DA model on test data:", accuracy_DA_test))
```

I will explore more information for LASSO model.

```{r}
# Extract coefficients from the fitted LASSO model
lasso_coefficients <- coef(lasso_model_optimal)

### 2024-05-04 products/manuscript/Manuscript copy.qmd
some minor errors

+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Model                            | Predictor                                                     | Metric Value  | Metric Value on testing data |
+==================================+===============================================================+===============+==============================+
| Linear null                      | \-                                                            | RMSE=8.01     | RMSE=7.99                    |
+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Linear regression 1              | Age, History, Alcohol, MTRANS                                 | RMSE=0.62     | RMSE=6.54                    |
+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Linear regression 2              | All                                                           | RMSE=6.29     | RMSE=3.81                    |
+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| LASSO model                      | All                                                           | RMSE=6.34     | RMSE=6.47                    |
|                                  |                                                               |               |                              |
|                                  |                                                               | l=0.023       |                              |
+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Random forest                    | All                                                           | RMSE=3.35     | RMSE=3.97                    |
+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Logistic null                    | \-                                                            | Accuracy=0.17 | Accuracy=0.15                |
+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Discriminant analysis            | Gender, Age, History, Water, Alcohol, FAF, MTRANS, Gender_Age | Accuracy=0.50 | Accuracy=0.50                |
+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Multinominal logistic regression | All                                                           | Accuracy=0.55 | Accuracy=0.50                |
+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+

@@

@@

@@

First, there is a problem with my outcome, BMI, which [could be misleading when being used as an indicator for obesity](https://www.yalemedicine.org/news/why-you-shouldnt-rely-on-bmi-alone), because BMI value could be misleading because a person with lots of muscle and minimal body fat can have the same BMI as a person with obesity who has much less muscle.
The other reason is that BMI was invented based on European white men and didn’t take into account that a person’s body fat also tends to vary depending on their sex, race, and ethnicity.
So it will be better to take fat content into consideration when doing analysis for obesity.
But it is not included.
The difficulty for obtaining fat content might be that it consumes time to measure with specific machine.
I did tried to do tuning for random forest model but I failed for running it successfully, so this could be a limitation that I have.
And maybe there could be more metrics that I can also calculate but I only chose 1 for each model.
Furthermore, chatGPT told me that even if testing result has a sign for well predicting, there still could be other factors for further assessment such as F1-score and so on.
But base on my understanding, I don't know what other methods I could choose from so I just stopped here.

>>>>

+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Model                            | Predictor                                                     | Metric Value  | Metric Value on testing data |
+==================================+===============================================================+===============+==============================+
| Linear null                      | \-                                                            | RMSE=8.01     | RMSE=7.99                    |
+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Linear regression 1              | Gender, Age, History, Water, Alcohol, FAF, MTRANS             | RMSE=6.42     | RMSE=6.54                    |
+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Linear regression 2              | All                                                           | RMSE=6.29     | RMSE=3.81                    |
+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| LASSO model                      | All                                                           | RMSE=6.34     | RMSE=6.47                    |
|                                  |                                                               |               |                              |
|                                  |                                                               | l=0.023       |                              |
+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Random forest                    | All                                                           | RMSE=3.35     | RMSE=3.97                    |
+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Logistic null                    | \-                                                            | Accuracy=0.17 | Accuracy=0.15                |
+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Discriminant analysis            | Gender, Age, History, Water, Alcohol, FAF, MTRANS, Gender_Age | Accuracy=0.50 | Accuracy=0.50                |
+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+
| Multinominal logistic regression | All                                                           | Accuracy=0.55 | Accuracy=0.50                |
+----------------------------------+---------------------------------------------------------------+---------------+------------------------------+

@@

A former study did research on a similar topic with this project, and the analysis indicated that among men, the proportional odds of obesity increase with urban residency, aging, marital status different from single and decrease with current smoking.
Among women, the proportional odds increase with urban residency, primary educational level, high total blood cholesterol level and high fasting blood glucose level, and decrease with current smoking [@kaboré2020].
It proved gender, age are risk or caustic factors for overweight or obesity, as well as other environmental factors and body conditions.

@@

For more detailed information of LASSO model, I took the review advice and tried to extract strongest and weakest coefficient, but the result showed that intercept was both strongest and weakest coefficient.
I didn't figure out how it could be interpret so it is not included in this part.

@@

First, there is a problem with my outcome, BMI, which [could be misleading when being used as an indicator for obesity](https://www.yalemedicine.org/news/why-you-shouldnt-rely-on-bmi-alone), because BMI value could be misleading because a person with lots of muscle and minimal body fat can have the same BMI as a person with obesity who has much less muscle.
The other reason is that BMI was invented based on European white men and didn’t take into account that a person’s body fat also tends to vary depending on their sex, race, and ethnicity.
So it will be better to take fat content into consideration when doing analysis for obesity.
But it is not included.
The difficulty for obtaining fat content might be that it consumes time to measure with specific machine.
Doing tuning for random forest model has been tried but I failed for running it successfully, so this could be a limitation.
And maybe there could be more metrics that I can also calculate but I only chose 1 for each model.
Furthermore, chatGPT said that even if testing result has a sign for well predicting, there still could be other factors for further assessment such as F1-score and so on.
But base on my understanding, I don't know what other methods I could choose from so I just stopped here.

### 2024-05-04 products/manuscript/supplement/Supplementary-Material.qmd
some minor errors

-   assets: storing reference pdf files and citation style files

-   data:

    -   raw-data: codebook created by me and original data file downloaded from website

    -   processed-data: cleaned data saved in RDS file

-   products: manuscript in qmd file and its render output with same name in doc file

-   R: including all codes needed

    -   analysis-code: including codes for simple exploratory analysis and machine learning models fitting both in qmd file and R script file

    -   eda-code: including codes for simple exploratory analysis and machine learning models fitting both in qmd file and R script file

    -   processing-code: including codes for data cleaning process both in qmd and R script file

-   renv: storage for all of the packages used in this project in R

-   results:

    -   figures: all of the plots in png file created and saved from eda-code and analysis-code

    -   tables: summary tables created and saved from eda-code and 2 linear model tables from analysis-code

>>>>

-   assets: storing reference pdf files and citation style file
-   data:
    -   raw-data: codebook created by me and original data file downloaded from website
-   processed-data: cleaned data saved in RDS file
-   products: manuscript in qmd file and its render output with same name in doc file
-   Rcode: including all codes needed
    -   analysis-code: including codes for simple exploratory analysis and machine learning models fitting both in qmd file and R script file
    -   dneda-code: including codes for simple exploratory analysis and machine learning models fitting both in qmd file and R script file
    -   mlmmodel-code: including codes for data cleaning process both in qmd and R script file
-   results:
    -   figures: all of the plots in png file created and saved from eda-code and analysis-code
    -   tables: summary tables created and saved from eda-code and 2 linear model tables from analysis-code
